Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2024-01-10 Manuscript_Nater_etal.qmd
Fixed spacing in MS and .bib

Detection decay parameters, which determine detection probability in distance sampling surveys, varied across areas from between `r Det.min$post.sum` in "`r Det.min$area.name`" to `r Det.max$post.sum` in "`r Det.max$area.name`, resulting in detection probabilities over the transect sites (truncation distance = 200 m) from `r pDet.min$post.sum` to `r pDet.max$post.sum`, respectively. The global average detection decay was `r Det.hyper.mean$post.sum` (detection probability = `r pDet.hyper.mean$post.sum`), and in general, higher values were more common in the Southern half of the country than the Northern half (SF"Avg_detect_Map.pdf"). Variation in detection over time was modest (SF "TimeSeries_pDetect.pdf"), and among-year variation in detection decay (random effect log SD = `r Det.sd.temporal$post.sum`) was almost identical in magnitude to spatial (`r Det.sd.spatial$post.sum`) and residual (`r Det.sd.residual$post.sum`) variation.

>>>>

Detection decay parameters, which determine detection probability in distance sampling surveys, varied across areas from between `r Det.min$post.sum` in "`r Det.min$area.name`" to `r Det.max$post.sum` in "`r Det.max$area.name`, resulting in detection probabilities over the transect sites (truncation distance = 200 m) from `r pDet.min$post.sum` to `r pDet.max$post.sum`, respectively. The global average detection decay was `r Det.hyper.mean$post.sum` (detection probability = `r pDet.hyper.mean$post.sum`), and in general, higher values were more common in the Southern half of the country than the Northern half (SF "Avg_detect_Map.pdf"). Variation in detection over time was modest (SF "TimeSeries_pDetect.pdf"), and among-year variation in detection decay (random effect log SD = `r Det.sd.temporal$post.sum`) was almost identical in magnitude to spatial (`r Det.sd.spatial$post.sum`) and residual (`r Det.sd.residual$post.sum`) variation.
